Rlearner_in_R

### 2025-07-30 codes/R/CF_Continuous_Loop.Rmd
commit changes before pull

# how many fields to train on?
n_fields <- 5

@@

x_vars    <- c("Nk", "plateau", "b0")
T_formula <- yield ~ s(N, k = 4)

# cf_results <- lapply(train_test_splits$test_id, function(test_sim_id)
cf_results <- lapply(train_test_splits$test_id, function(test_sim_id) {
  result_file <- file.path(output_dir, paste0("sim_", test_sim_id, ".rds"))
  if (file.exists(result_file)) {
    message(sprintf("Skipping sim %d (already saved)", test_sim_id))
    return(NULL)
  }

  tryCatch({

    split_row     <- train_test_splits[train_test_splits$test_id == test_sim_id, ]
    train_sim_ids <- as.integer(unlist(split_row[paste0("train_", 1:n_fields)]))

@@

    # fit causal forest
    T_info     <- prepare_T_mat(T_formula, train_data)
    Y          <- train_data[, yield]
    X          <- train_data[, ..x_vars] %>% as.matrix()
    W          <- X
    te_hat_cf  <- run_CF_c_py(Y, T_info$T_sp, X, W, n_estimators = 2000)
    te_info    <- get_te(te_hat_cf, test_data, x_vars)

@@

    # true EONR
   true_eonr <- raw_sim_data$reg_data[[1]] %>%

  .[sim == test_sim_id, ] %>%

  .[, .(sim, data)] %>%
  unnest(cols = c(data)) %>%
  data.table() %>%
  .[, .(aunit_id, b0, b1, b2, Nk)] %>%
  .[, opt_N := (pN / pCorn - b1) / (2 * b2)] %>%
  .[, opt_N := pmin(Nk, pmax(0, opt_N))] %>%
  .[, .(aunit_id, opt_N)]

@@

  }, error = function(e) {
    message(sprintf("Error with sim %d: %s", test_sim_id, e$message))
    data.table(
      sim        = test_sim_id,
      aunit_id   = integer(),
      opt_N_hat  = numeric(),
      opt_N      = numeric()
    )
  })
})

>>>>

# how many fields to train on?
n_fields <- 1

@@

x_vars    <- c("Nk", "plateau", "b0")
#T_formula <- yield ~ s(N, k = 4)
T_formula <- y_tilde ~ s(N, k = 4)
# cf_results <- lapply(train_test_splits$test_id, function(test_sim_id)
cf_results <- lapply(train_test_splits$test_id, function(test_sim_id) {
  result_file <- file.path(output_dir, paste0("sim_", test_sim_id, ".rds"))
  if (file.exists(result_file)) {
    message(sprintf("Skipping sim %d (already saved)", test_sim_id))
    return(NULL)
  }

  tryCatch({
    # grab exactly n_fields train IDs for this test
    # base‐R subsetting – unambiguous
    split_row     <- train_test_splits[train_test_splits$test_id == test_sim_id, ]
    train_sim_ids <- as.integer(unlist(split_row[paste0("train_", 1:n_fields)]))

@@

    # fit causal forest
    T_info     <- prepare_T_mat(T_formula, train_data)
    Y          <- train_data[, y_tilde]
    X          <- train_data[, ..x_vars] %>% as.matrix()
    W          <- X
    te_hat_cf  <- run_CF_c_py(Y, T_info$T_sp, X, W, n_estimators = 2000)
    te_info    <- get_te(te_hat_cf, test_data, x_vars)

@@

    # true EONR
   true_eonr <- raw_sim_data$reg_data[[1]] %>%
  # 1) keep only this sim
  .[sim == test_sim_id, ] %>%
  # 2) grab the nested data column
  .[, .(sim, data)] %>%
  # 3) unnest into rows
  unnest(cols = c(data)) %>%
  # 4) coerc e to data.table so you can use [ , … ]
  data.table() %>%
  # 5) pull out just the columns you need
  .[, .(aunit_id, b0, b1, b2, Nk)] %>%
  # 6) compute true opt_N
  .[, opt_N := (pN / pCorn - b1) / (2 * b2)] %>%
  .[, opt_N := pmin(Nk, pmax(0, opt_N))] %>%
  # 7) keep only the ID + opt_N
  .[, .(aunit_id, opt_N)]

@@

  }, error = function(e) {
    message(sprintf("Error with sim %d: %s", test_sim_id, e$message))
    data.table(
      sim        = test_sim_id,
      aunit_id   = integer(),
      opt_N_hat  = numeric(),
      opt_N      = numeric()
    )
  })
})
```
